### 2017-02-26 2017mergingmerges/section/03-Definition.tex
ins instrs and the next updates need to be maps not sets, as we cant have elems with duplicate keys

\clearpage{}
\section{Process definitions}

@@

A $\Proc$ is a record with five fields: the @ins@ field specifies the input channels; the @outs@ field the output channels; the @heap@ field the process-local heap; the @label@ field the label of the currently being executed instruction, annd the @instrs@ the set of labeled instructions. We use the same record when specifying both the definition of a particular process, as well as when giving the evaluation semantics. When specifying a process the @label@ field gives the entry-point to the process code, though during evaluation it is the label of the instruction currently being executed. Likewise, when specifying a process we usually only list channel names in the @ins@ field, though during evaluation they are also paired with their current $\InputState$. If an $\InputState$ is not specified we assume it is `none'.

@@

The @instrs@ field of the $\Proc$ maps labels to instructions. The possible instructions are: @pull@, which pulls the next value from a channel into a given heap variable; @push@, which pushes the value of an expression to an output channel; @case@ which branches depending on the result of a boolean expression; @jump@ causes control to move to a new instruction, and @drop@ which indicates that the current value pulled from a channel is no longer needed.

All instructions include a $\Next$ field which is a pair of the label of the next instruction to execute, as well as a list of $\Var \times \Exp$ bindings which are used to update the heap. The update bindings are attached directly to instructions to make the fusion rules easier to specify, in contrast to a presentation with a separate @update@ instruction.

@@

Evaluation of processes and process networks is split into three parts:
\begin{itemize}
\item Injection, where a single value for a stream is inserted into a process' input buffer.
Injection is only possible when the process' input buffer is empty, or the process ignores that stream.
Injection for a process network proceeds by injecting the same value into all processes in the network.

@@

\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} defines the judgment forms and rules for injection.
Injection is used by the other parts of evaluation to \emph{inject} stream values into a process' input buffer.

@@

\subsubsection{Shaking}
Fig.~\ref{fig:Process:Eval:Shake} defines the judgment forms and rules for shaking a process, allowing it to take a step, and produce an output message.
% I don't like them, but alpha and tau are standard names in process calculi. 
The type of messages is denoted by $\alpha$, which can either be ($\Push~\Chan~\Value$) for pushing a value to a particular channel, or $\tau$ for an `internal' message which only performs local state updates.

@@

\subsubsection{Feeding}
Fig.~\ref{fig:Process:Eval:Feed} defines the judgment forms and rules for feeding, where external input values are fed into a process network and output values are accumulated.
The judgment form for feeding is $\ProcsFeed{\ti{inputs}}{\ti{network}}{\ti{streams}}{\ti{network}'}$.
The input map $\ti{inputs}$ contains values for the network inputs: network outputs are not allowed, but ignored channels can have values.
The result $\ti{streams}$ contains the original inputs as well as accumulated output values.
Feeding evaluates the process network until all input values have been injected.

>>>>

\clearpage{}
% -----------------------------------------------------------------------------
\section{Process definitions}

@@

A $\Proc$ is a record with five fields: the @ins@ field specifies the input channels; the @outs@ field the output channels; the @heap@ field the process-local heap; the @label@ field the label of the currently being executed instruction, and the @instrs@ a map of labels to instructions. We use the same record when specifying both the definition of a particular process, as well as when giving the evaluation semantics. When specifying a process the @label@ field gives the entry-point to the process code, though during evaluation it is the label of the instruction currently being executed. Likewise, when specifying a process we usually only list channel names in the @ins@ field, though during evaluation they are also paired with their current $\InputState$. If an $\InputState$ is not specified we assume it is `none'.

@@

The @instrs@ field of the $\Proc$ maps labels to instructions. The possible instructions are: @pull@, which pulls the next value from a channel into a given heap variable; @push@, which pushes the value of an expression to an output channel; @case@ which branches depending on the result of a boolean expression; @jump@ which causes control to move to a new instruction, and @drop@ which indicates that the current value pulled from a channel is no longer needed.

All instructions include a $\Next$ field which is a pair of the label of the next instruction to execute, as well as a map of heap $\Var$ to $\Exp$ which is used to update the heap. The map of update expressions is attached directly to instructions to make the fusion algorithm easier to specify, in contrast to a presentation with a separate @update@ instruction.

@@

Evaluation of processes and process networks is split into three parts:

\begin{itemize}
\item Injection, where a single value for a stream is inserted into a process' input buffer.
Injection is only possible when the process' input buffer is empty, or the process ignores that stream.
Injection for a process network proceeds by injecting the same value into all processes in the network.

@@

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} defines the judgment forms and rules for injection.
Injection is used by the other parts of evaluation to \emph{inject} stream values into a process' input buffer.

@@

% Injecting requires the input buffer to be empty or the process to ignore that channel.
For networks, all processes must successfully inject the value.

% -----------------------------------------------------------------------------
\subsubsection{Shaking}
Fig.~\ref{fig:Process:Eval:Shake} defines the judgment forms and rules for shaking a process, allowing it to take a step, and produce an output message.
% I don't like them, but alpha and tau are standard names in process calculi. 
The type of messages is denoted by $\alpha$, which can either be ($\Push~\Chan~\Value$) for pushing a value to a particular channel, or $\tau$ for an `internal' message which only performs local state updates.

@@

% -----------------------------------------------------------------------------
\subsubsection{Feeding}
Fig.~\ref{fig:Process:Eval:Feed} defines the judgment forms and rules for feeding, where external input values are fed into a process network and output values are accumulated.
The judgment form for feeding is $\ProcsFeed{\ti{inputs}}{\ti{network}}{\ti{streams}}{\ti{network}'}$.
The input map $\ti{inputs}$ contains values for the network inputs: network outputs are not allowed, but ignored channels can have values.
The result $\ti{streams}$ contains the original inputs as well as accumulated output values.
Feeding evaluates the process network until all input values have been injected.
